### 2019-12-22 article.tex
a mistake in tables fixed
discussion improved

		\IF {$ P_{i} \geq 0.5$}
		\STATE $\hat{Y}_i \gets \;$ Healthy Control
		\ELSE
		\STATE $\hat{Y}_i \gets \;$ Parkinson's
		\ENDIF

@@

\begin{table}
	\caption{Comparison of the proposed method with 2 other rivals}
	\begin{tabular}{| c | c | c | c | }
		\hline
		Method & \shortstack{Average \\ accuracy (\%)} & \shortstack{Average \\ time (min)} & \shortstack{Test \\ hardware} \\ \hline

		Proposed Method & 97.92 & 72.06 & GPU \tiny{(GTX1080)} \\
		Sarraf and Tofighi & 45.83 & 407.6 & CPU \tiny{(Intel4710HQ)} \\
		Rashid et al.          & 58.33 & 23.13 & CPU \tiny{(Intel4710HQ)} \\ \hline
	\end{tabular}
	\label{table:comparison}
\end{table}

@@

Without

>>>>

		\IF {$ P_{i} \geq 0.5$} \label{alg:proposedMethod:threshold}
		\STATE $\hat{Y}_i \gets \;$ Healthy Control
		\ELSE
		\STATE $\hat{Y}_i \gets \;$ Parkinson's
		\ENDIF

@@

\begin{table}
	\caption{Comparison of the proposed method with 2 other rivals}
	\resizebox{\linewidth}{!}{%
	\begin{tabular}{| c | c | c | c | }
		\hline
		Method & \shortstack{Average \\ accuracy (\%)} & \shortstack{Average \\ time (min)} & \shortstack{Test \\ hardware} \\ \hline

		Proposed Method & 97.92 & 72.06 & CPU \tiny{(Intel4710HQ)} \\
		Sarraf and Tofighi & 45.83 & 407.6 & GPU \tiny{(GTX1080)} \\
		Rashid et al.          & 58.33 & 23.13 & CPU \tiny{(Intel4710HQ)} \\ \hline
	\end{tabular}
}
	\label{table:comparison}
\end{table}

@@

The proposed method has shown better results in Parkinson's disease diagnosis task compared to two other methods which can be seen in Table \ref{table:comparison}. However, Rashid et al. SVM based method is approximately 3 times faster and in case of time efficiency and speed, it seems far better. On the other hand, Sarraf and Tofighi's method demands a powerful processing unit alongside a huge amount of time. Finally, the proposed method is the most accurate undoubtedly and can solve the problem in a reasonable time.

We can change, tune and improve a lot of factors from Algorithm \ref{alg:proposedMethod}. First of all, the threshold of healthiness at line~\ref{alg:proposedMethod:threshold} can change to any other number instead of $0.5$, which may require advice from a consultant or a doctor. Also, dropout probabilities are important and somehow hard to find any rule for them. We did some experiments and mentioned probabilities were good enough to solve the problem. In addition to that, it is possible to change network architecture by manipulating parameters such as the number of filters and the size of kernels in pooling and convolution layers.
